% mongodb-tcc.tex

% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm]{acmart}
\input{preamble}
\input{newcommands}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{14}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2020}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle}
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{URL_TO_YOUR_ARTIFACTS}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain}

\begin{document}
\title{Design and Implementation of Transactional Causal Consistency in MongoDB}

%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
\author{xxx}
\affiliation{%
  \institution{State Key Laboratory for Novel Software Technology}
}
\affiliation{%
  \institution{Nanjing University}
  \city{Nanjing}
  \country{China}
}
\email{xxx@smail.nju.edu.cn}

\author{xxx}
\affiliation{%
  \institution{State Key Laboratory for Novel Software Technology}
}
\affiliation{%
  \institution{Nanjing University}
  \city{Nanjing}
  \country{China}
}
\email{xxx@smail.nju.edu.cn}

\author{Hengfeng Wei$^*$}\titlenote{Corresponding author.
Hengfeng Wei is also with Software Institute at Nanjing University.}
\affiliation{%
  \institution{State Key Laboratory for Novel Software Technology}
}
\affiliation{%
  \institution{Nanjing University}
  \city{Nanjing}
  \country{China}
}
\email{hfwei@nju.edu.cn}

\author{Yu Huang}
\affiliation{%
  \institution{State Key Laboratory for Novel Software Technology}
}
\affiliation{%
  \institution{Nanjing University}
  \city{Nanjing}
  \country{China}
}
\email{yuhuang@nju.edu.cn}

\author{$\dots$}
\affiliation{%
  \institution{}
}
\email{}

\author{$\dots$}
\affiliation{%
  \institution{}
}
\email{}

\input{sections/abstract}

\maketitle

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\pagestyle{\vldbpagestyle}
\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\endgroup
\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150-8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\ifdefempty{\vldbavailabilityurl}{}{
\vspace{.3cm}
\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
\endgroup
}
%%% VLDB block end %%%

\input{sections/intro}
\input{sections/preliminaries}
\input{sections/related-work}
\input{sections/conclusion}
% \input{sections/ack}

%\clearpage

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{mongodb-tcc}

\end{document}
\endinput
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%